On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-11-17 paper/paper.tex
clean up sentence in abstract

\begin{abstract}
% Say what problem is
  Capturing control flow is the Achilles heel of Haskell-based
  deeply embedded domain specific languages.
  Rather than use
  the builtin control flow mechanisms, artificial control flow combinators
  are used instead.
% Say why it is an interesting problem
  However, capturing traditional control flow in a deeply embedded domain specific language
  would support the writing of programs in a natural style by allowing the programmer to use the
  constructs that are already builtin to the base language, such as pattern
  matching and recursion.
% Say what our solution achieves
  In this paper, we expand the capabilities of
  Haskell-based deep embeddings with a compiler extension
  for reifying conditionals and pattern matching.
% Here is why the world will be a better place
  With this new support, the Haskell that we capture for expressing
  deeply embedded domain specific languages can be cleaner, Haskell-idiomatic,
  and more declarative in nature.

>>>>

\begin{abstract}
% Say what problem is
  Capturing control flow is the Achilles heel of Haskell-based
  deeply embedded domain specific languages.
  Rather than use
  the builtin control flow mechanisms, artificial control flow combinators
  are used instead.
% Say why it is an interesting problem
  However, capturing traditional control flow in a deeply embedded domain specific language
  would support the writing of programs in a natural style by allowing the programmer to use the
  constructs that are already builtin to the base language, such as pattern
  matching and recursion.
% Say what our solution achieves
  In this paper, we expand the capabilities of
  Haskell-based deep embeddings with a compiler extension
  for reifying conditionals and pattern matching.
% Here is why the world will be a better place
  With this new support, the subset of Haskell that we use for expressing
  deeply embedded domain specific languages can be cleaner, Haskell-idiomatic,
  and more declarative in nature.
